\documentclass[12pt]{article}
 
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
 
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
 
\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\newenvironment{solution}{\begin{proof}[Solution]}{\end{proof}}
 
\begin{document}
 
\title{PS9}
\author{Adam Matthies\\}

\maketitle

\section{Modeling Questions}


\begin{enumerate}
\item The optimal value of lambda for LASSO was .001 and the in-sample RMSE was 0.413. The
out-of-sample RMSE was 0.390.
\item The optimal value of lambda for Ridge was 0.00464 and the out-of-sample RMSE was 0.167.

\end{enumerate}

The ridge regression seemed a lot more accurate because all of the independent variables needed to 
be kept to give accurate predictions of home values. My lasso shrunk about every variable to 0
due to the penalty of .001 so I am convinced my optimization may have been done incorrectly. However,
for this dataset, I do believe a ridge regression makes more sense to use--which can be seen in the
out-of-sample RMSE. 

No, you cannot have more observations than predictors in a simple linear regression. The RMSE from
the ridge was quite low, so it shows a good tradeoff between bias and variance. The lasso RMSE was
higher, so it is either showing an issue of overfitting or underfitting the data.

 
\end{document}
