\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{PS1}
\author{Adam Matthies}

\begin{document}
\maketitle

\section{Introduction}

My interests in economics primarily include econometrics and monetary policymaking. However, monetary policymaking is more of a hobby that I like to follow rather than something I would look to pursue a career in. In data science, I am intrigued by the optimization of problems and the ability to make better decisions with the use of machine learning models. I am taking this class because my knowledge of ML is very elementary and I am taking this class as a step to improve my skills in data and ML techniques. My goal for this class is to become much more acquainted with data collection and coding. I am concurrently taking math courses and hope to be able to better use computer software to model large datasets with math techniques I am also learning. For the class project, I will probably do something in macroeconomics in monetary policymaking or maybe something in baseball statistics--as I have been a huge fan of baseball stats since grade school and the MLB Savant page is rich in any sort of data. After graduation, I would like to do something in business that helps with forecasting future outcomes or using math to optimize functions -- as everything follows the laws of calculus and physical law.

\subsection{Equation}

\[ a^2 + b^2 = c^2 \]

\end{document}